A Longitudinal Analysis of the Privacy Paradox

### 2019-09-19 analyses/analyses.Rmd
- small language edits to manuscript - small changes to abstract - small changed to analysis file; e.g., updated order of analyses

### Latent correlation matrix with plots

@@

```{r}
fit <- lmer(pri_con_m ~ 1 + (1 | id), filter(d_long, wave < 4))
summary(fit)
icc_pri_con <- icc(fit)

fit <- lmer(inf_sha_att_m ~ 1 + (1 | id), filter(d_long, wave < 4))
summary(fit)
icc_inf_sha_att <- icc(fit)

fit <- lmer(inf_sha_beh_m ~ 1 + (1 | id), filter(d_long, wave < 4))
summary(fit)
icc_inf_sha_beh <- icc(fit)
```

@@

>>>>

# Correlation matrix and distributions

@@

```{r}
fit <- lmer(pri_con_m ~ 1 + (1 | id), filter(d_long, wave < 4))
summary(fit)
(icc_pri_con <- icc(fit))

fit <- lmer(inf_sha_att_m ~ 1 + (1 | id), filter(d_long, wave < 4))
summary(fit)
(icc_inf_sha_att <- icc(fit))

fit <- lmer(inf_sha_beh_m ~ 1 + (1 | id), filter(d_long, wave < 4))
summary(fit)
(icc_inf_sha_beh <- icc(fit))
```

@@

## Visualization

## Results

# control variables
t1_pri_con_fs ~ age + edu_num + male
t2_pri_con_fs ~ age + edu_num + male
t3_pri_con_fs ~ age + edu_num + male
t1_inf_sha_beh_fs ~ age + edu_num + male
t2_inf_sha_beh_fs ~ age + edu_num + male
t3_inf_sha_beh_fs ~ age + edu_num + male
t1_inf_sha_att_fs ~ age + edu_num + male
t2_inf_sha_att_fs ~ age + edu_num + male
t3_inf_sha_att_fs ~ age + edu_num + male
'
fit <- sem(model, data = d_wide, orthogonal = TRUE, missing = "ML")
summary(fit, standardized = TRUE, fit.measures = TRUE, ci = TRUE)
```
